---
title: "Programming a Little App"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Programming a Little App}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LittleApp2)
```

For each app,  in `app-specific-services.R`, there should be these
**reactives**:

- `main_calculation()`  Returns a list with three items:
   1. `main` - a  plot
   2. `side` - another plot (or `NULL`  if you  don't need one)
   3. `stats` - a data frame or list containing the statistics to display. If there is an error or some reason that the stats cannot be calculated, you  have a choice of dealing with this in  the `format_stats()` function (see below) or by having `main_calculation()` return a `stats` component that is an HTML string  rather than a list/data-frame. 
- `model_formula()` Returns a model formula  suitable for the app.
- A reactive triggered by `input$show_app_params` that produces a modal dialog allowing the user to set parameters. In the Shiny  input  widgets, use the values stored in `Common` (see below) to initialize each parameter.
- `Common`. A reactiveValue containing elements with the  same names as in the parameter-setting modal frame. For each of these, there also needs
to be an `observeEvent()` that sets the value of the `Common` element whenever the `input` is changed, e.g. 
```r
observeEvent(input$selected_category,  {
  Common$selected_category <<- input$selected_category
})
```
The elements of `Common` should be initialized to the default values for each.

`app-specific-services.R` should also contain a non-reactive function (that is, an ordinary R  function) that takes the `stats` component returned by `main_calculation()` and formats it into an HTML string for display. It's helpful  if the string is visually narrow, since both the current and frozen stats will be shown side-by-side.

# To do !!!



# Overview

A Little App is a particular layout of Shiny app, consisting of several tabs and a top toolbar with items that are visible regardless of which tab is active. Typical tabs are

1. explain: rendering HTML documentation describing the app
2. data: providing a means to select a dataset and the response and explanatory variables to be displayed
3. graph: the central graph showing the display at full size
4. compare: like (3) but shows the display for both  the current graph and one that may have been frozen early.
5. stats: a column of statistical report for both the current and frozen display
6. codebook: showing the codebook for the selected data set
7. debug: a place to print out intermediate results for debugging purposes


## The app's personality

Defining the `main_calculation()` reactive.

RETURNS two plots in a list, `main` and `side`. Might return other stuff in the list as well, stuff you could  use  in  the `app_specific_services.R` list.


## Data services



### Inputs

1. `input$package`: text. Which package to get the data from. 
1. `input$frame`: text. Which data frame within the package
1. `input$response`: text. Which variable from the frame.
2. `input$explanatory` text. Which  variable from the frame.
3. `input$covariate` text. Which variable from the frame. Optional. Set in `data_tab()`.
4. `input$covariate2` text. Which variable from the frame. Optional. Set in `data_tab()`.
1. `input$stratify`: logical, whether to stratify sampling by  the explanatory variables.

### Reactives you can use

1. `raw_data()`: returns the whole data frame, all variables. There may be NAs.
2. `current_sample()`: returns the current sample, containing only the selected variables.
    - The variables will always be in order: response, explanatory, covariate, covariate2
    - The NA's have been filtered out
3. `frozen_sample()`: the last sample frozen.
5. `frozen_calculation()`:  this is provided automatically, based on saving a result from your `main_calculation()`

### Reactives and renders you  need to define

1. `main_calculation()`: *provided by the app  writer*.
1. `output$current_stats`: Must be HTML and protected with `HTML()`
2. `output$frozen_stats`: presumably identical, but with the frozen data.

All the plot outputs are filled in automatically from the results of your  `main_calculation()` reactive

### Modals you construct

All of the inputs you need for your `main_calculation()` go in these modals. They are modals so that you  can make them  as large as you need without upsetting the standard  layout of the app.

These are generated from Shiny input widgets. Each may contain either informative text, output widgets,  or input widgets.

If they are input widgets, you  should cash each input  value  under the  `Common` reactive value.

LUMP THESE TOGETHER.  WE ONLY NEED ONE.
1. Modal for `input$show_model`
2. Modal for `input$show_annotation`

## Toolbar inputs

You  put the inputs you need for your calculations in  the modals that you construct. You'll most likely use these in  your `main_calculation()` function.


Other inputs are built in and used  by reactives such  as `raw_data()` and `current_sample()`. They are listed below, but you should not usually need to access these directly.

1. `input$sample_size`: the size n of the desired sample
2. `input$randomize`: if true, shuffle the response variable
3. `input$new_sample`: trigger to collect a new random sample
4. `input$freeze`: trigger to save the current sample/model/etc. in the frozen display

